Flabby and injective objects in toposes

### 2018-10-21 paper-flabby-objects.tex
Detail's on Harting's proof

The analogue of Theorem~\ref{thm:injectivity-external-internal} for modules
holds as well, if~$\E$ is assumed to have a natural numbers object. The proof
carries over word for word, only referencing
Lemma~\ref{lemma:set-of-extensions-flabby}(2) instead of
Lemma~\ref{lemma:set-of-extensions-flabby}(1).
It seems that Roswitha Harting was not aware of this generalization, even though she did show that
injectivity of sheaves of modules over topological spaces is a local
notion~\cite[Remark~5]{harting:remark}, as she
(mistakenly) states in~\cite[page~233]{harting:remark} that ``the notions of
injectivity and internal injectivity do not coincide'' for modules.
% XXX comparison with Harting's proof (Barr's lemma...)

>>>>

The analogue of Theorem~\ref{thm:injectivity-external-internal} for modules
holds as well, if~$\E$ is assumed to have a natural numbers object. The proof
carries over word for word, only referencing
Lemma~\ref{lemma:set-of-extensions-flabby}(2) instead of
Lemma~\ref{lemma:set-of-extensions-flabby}(1).
It seems that Roswitha Harting was not aware of this generalization, even though she did show that
injectivity of sheaves of modules over topological spaces is a local
notion~\cite[Remark~5]{harting:remark}, as she
(mistakenly) states in~\cite[page~233]{harting:remark} that ``the notions of
injectivity and internal injectivity do not coincide'' for modules.

It is worth noting that, because the internal language machinery was at that
point not as well-developed as it is today, she had to go to considerable
length to construct internal direct sums of abelian group
objects~\cite{harting:coproduct}, and in order to verify that taking internal
direct sums is faithful she felt the need to employ Barr's
metatheorem~\cite[Theorem~1.7]{harting:effacements}. Nowadays we can verify
both statements by simply carrying out an intuitionistic proof in the case of
the topos of sets and then trusting the internal language to obtain the
generalization to arbitrary elementary toposes with a natural numbers object.
